Reproducible Research Peer-Review Excercise 1 
========================================================

Excercise submitted by Rajeev Vij
Thanks for reviewing

## Step 1 Read data file and produce summary information

```{r}

activity <- read.csv("activity.csv", sep=",", header=TRUE, stringsAsFactors=FALSE)
head(activity)
summary(activity)
```

## Step 1 Draw chart for total steps per day and avg steps per interval excluding missing data

```{r}
library(sqldf)

ex1 <- sqldf("select date, sum(steps) as steps_per_day from activity where steps <> 'NA' group by date")

library(ggplot2)

qplot(steps_per_day, data=ex1, geom="histogram", binwidth=1000)

ex2 <- sqldf("select interval, avg(steps) as avg_steps from activity where steps <> 'NA' group by interval")

maxval <- ex2[ex2$avg_steps == max(ex2$avg_steps), ]

ggplot(ex2, aes(ex2$interval, ex2$avg_steps)) + geom_line() + 
  geom_vline(xintercept=maxval$interval) +
  annotate("text", x = maxval$interval:maxval$interval, y = 0, label = as.character(maxval$interval))
````

## Step 3 Impute missing data and draw total steps per interval and produce summary
```{r}
activity_nona <- activity
sum(is.na(activity_nona$steps))

naindx <- which(is.na(activity_nona$steps))

for (i in naindx){
  activity_nona$steps[i] <- ex2[ex2$interval == activity_nona$interval[i],"avg_steps" ]
}

ex11 <- sqldf("select date, sum(steps) as steps_per_day from activity_nona where steps <> 'NA' group by date")

qplot(steps_per_day, data=ex11, geom="histogram", binwidth=1000)

summary(activity_nona)
```

## Step 4: Add a factor variable daytype and produce facetd plot of avg_steps per interval 
```{r}
activity_nona$daytype <- as.factor(sapply(as.Date(activity_nona$date), function(d) {if(weekdays(d) %in% c("Saturday", "Sunday")) "Weekend" else "Weekday"}))

table(activity_nona$daytype)

ex3 <- sqldf("select daytype, interval, avg(steps) as avg_steps from activity_nona group by daytype, interval")

p <- ggplot(ex3, aes(interval,avg_steps)) + geom_line()
p + facet_grid(daytype ~ .)

```

